\vspace{50pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-12 analytics.tex
Analytics

  \item Skedge’s \textbf{DSQL is user-friendly}; users learn more advanced search types over time \textbf{simply by using it}.
\end{enumerate}

@@

\begin{itemize}
  \item 4,713 users that have added or bookmarked at least 1 course
  \item 5,256 schedules
  \item 17,012 sessions\footnote{A session is defined by a period of activity expiring after 30 minutes of inactivity}, 75\% of which are from returning visitors
  \item 107 sessions per day, on average
  \item 5.40 pages viewed per session, on average 
  \item 6 minutes spent per session, on average
\end{itemize}

@@

  \caption{Etc}
  \label{fig:searches}

@@

periodic visit cycle graph means people are actually using it and decided to stay with it, not declining, can be seen w exports & link-searches.

also should be noted that NO seniors participated in the last, the majority of the userbase!

success Considering skedge is OPTIONAL.

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{images/graph/exports}

@@

@@

  \begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{images/graph/searchtypes}

  Can learn from these
  Some funny ones

@@

  Why would 0-navs be so common with direct searches? 65\% subsections!

@@

  % STAT: Find major of users, find how many non-major courses they found

@@

  As expected, the 0-navs were mostly maincourses

@@

First increase (60.5\% of users)
Median: 2 searches
Average: 4.23 searches
(Starting at 1 counts as an increase value of 0)

>>>>

  \item Skedge’s \textbf{DSQL is user-friendly}; users learn how to make more sophisticated search queries over time \textbf{simply by using it}.
\end{enumerate}

@@

\begin{itemize}
  \item 4,713 users that have added or bookmarked at least one course
  \item 5,256 schedules
  \item 17,124 sessions\footnote{A session is defined by a period of activity expiring after 30 minutes of inactivity}, 75\% of which are from returning visitors
  \item an average of 107 sessions per day
  \item an average of 5.4 pages viewed per session 
  \item an average of 6 minutes spent per session
\end{itemize}

\begin{figure}[H]
  \centering

@@

  \caption{Searches over time, with major relevant calendar events annotated}
  \label{fig:searches}

@@

Figure \ref{fig:searches} shows user search submissions over the time, and makes the periodicity of Skedge usage extremely apparent. Although it only shows a bit more than one ``phase,'' the cycle of events---\emph{semester begins} (students check course times, room locations, etc. while they get accustomed to the semester), \emph{next semester's course catalog released} (students explore the courses offered and build possible schedules), \emph{next semester registration opens} (cross-checking and officially registering each course with the Registrar)---clearly drives the majority of site traffic.

What this means is that Skedge is not seen as an experiment or a proof of concept that is not production-ready. Rather, its traffic patterns show that it is consistenly \emph{relied upon} by students and used for its intended purpose in times of biggest course scheduling need. %, and the same can be seen with other usage measures such as schedule exporting and clicking on the Wikipedia-style embedded links (Figures \ref{fig:exports} and \ref{fig:linksearches}, respectively).

It should also be noted that before March, the majority of the userbase as I knew it consisted of seniors, as the majority of people that I knew personally and shared Skedge with belonged to my class. The latest two major events reported in the graph above thus very impressively consist of \emph{very few seniors}, who have no courses left to schedule. March also marked the very first time I publicly advertised Skedge, although not very strongly. It was sent out to all students in the Computer Science mailing list as well as posted to two class-wide Facebook groups.

The usability of and user satisfaction with a tool is hard to measure when it holds a monopoly. Considering that Skedge is an \emph{optional alternative} to CDCS, such consistent usage data (especially with 75\% of sessions being from returning users) undeniably prove its measures of usability and user satisfaction relative to CDCS.

  \begin{figure}[H]
    \centering
    \includegraphics[width=1.0\textwidth]{images/graph/searchtypes}

    \caption{Breakdown of search queries by type of search}
    \label{fig:searchtypes}
  \end{figure}

Figure \ref{fig:searchtypes} validates the hypothesis made in Section 2.3 regarding the search interface design, demonstrating that the \emph{department code} and \emph{course number} search modes dominate user searches, accounting for over 85\% of all searches on Skedge. With this knowledge, bringing out the tucked-away, nondistinct field for this search in CDCS into prominence is a usability design choice that accomodates empirical usage.

  Of the total 45,466 searches on Skedge logged since November 2nd 2015, 89.4\% (40,625) of searches produce nonempty search results, whereas 10.6\% (4,841) of searches come up empty. This already is evidence of an effective search mechanism, but of those empty searches, the vast majority

  Can learn from these searches.

  \begin{figure}
  {\renewcommand{\arraystretch}{1.5}
  \centering
  \begin{tabular}{ p{6cm} p{7.5cm} }
  \hline

    ``{\tt Prereq 280}'' \newline ``{\tt has-Prereq: 280}''
    & Course dependencies \\ \hline

    ``{\tt tuesday 3:25-4:40}'' \newline ``{\tt TR 3:25-4:40}'' \newline ``{\tt m/w}'' \newline ``{\tt classes tuesdays and thursdays between 11:05 and 12:20}'' \newline ``{\tt weekend summer 2016}''
    & \parbox[c]{\hsize}{Better day-of-the-week handling} \\ \hline

    ``{\tt 2 credits natural science}'' 
    & Search by division (although there were very few) \\ \hline

    ``{\tt religion and classics}'' \newline ``{\tt studio art}'' 
    & Search by full department name \\ \hline

    ``{\tt new csc courses}'' 
    & The word ``{\tt courses}'' (somewhat common) \\ \hline

    ``{\tt guo}'' 
    & Instructor without ``{\tt taught by}'' (very common) \\ \hline

    ``{\tt stt212 vs mth201}'' \newline ``{\tt stt212 OR mth201}'' 
    & Searching multiple queries at the same time \\ \hline

    ``{\tt crosslisted csc lin}'' 
    & Probably a more reasonable syntax than the current Skedge DSQL one (``{\tt csc x lin}'') \\ \hline

    ``{\tt place: hubbell}'' \newline ``{\tt hubbell friday}'' 
    & Search by location, although motives unclear \\ \hline

    ``{\tt MTH 2*}'' 
    & Using ``{\tt *}'' instead of an omission (e.g. ``{\tt MTH 2}'' would work) \\ \hline

    \hline
  \end{tabular}
  \caption{Example of search queries that produced no results but that indicate demand for added search features. The corresponding features that currently lack in the Skedge DSQL are described on the right.}
  \end{figure}

\begin{figure}
  {\renewcommand{\arraystretch}{1.5}
  \centering
  \begin{tabular}{ | p{4cm} | p{4cm} | p{4cm} | }
  \hline

    ``{\tt Larry david}''
    & ``{\tt taught by seligman}''
    & ``{\tt cool stuff}''
    \\ \hline

    ``{\tt game of thrones}''
    & ``{\tt fun classes}''
    & ``{\tt fun classes in csc}''
    \\ \hline

    ``{\tt easy A}''
    & ``{\tt flute birdman}''
    & ``{\tt how do i make a new schedule}''
    \\ \hline

    \hline
  \end{tabular}
  \caption{Humerous search submissions}
  \end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1.0\textwidth]{images/graph/exports}

  \caption{Etc}
  \label{fig:exports}
\end{figure}

@@

  \caption{Etc}
  \label{fig:linksearches}
\end{figure}

@@

@@

  Why would 0-navs be so common with direct searches? 64\% of them subsections!

@@

@@

  As expected, the 0-navs were mostly maincourses (62\%)

@@

First increase 69.4\% of users), with a median of 2 searches.
Note that starting at search complexity one or greater counts as a ``searches before first increase value'' of 0.

### 2016-04-12 conclusion.tex
Analytics

On behalf of myself and the roughly \emph{one-thousand} students that regularly and voluntarily choose to use Skedge, I urge the University to consider adopting it as an official replacement to CDCS.

Given the excellence of the University's inspiring faculty and academic programs, I know that I am not alone in my disappointment with what I find is a lack of regard for many student tools, as well as the lack of communication channels with students to improve them. Throughout the course of this paper, I have shown that the space of course scheduling holds vast potential for innovation, and that CDCS barely scratches that surface. An officially adopted Skedge---or an otherwise substantial overhaul of CDCS---would demonstrate that the University pays attention to its students and to how they use the tools it provides them.

>>>>

On behalf of myself and the roughly \emph{one-thousand} students who regularly and voluntarily choose to use Skedge, I urge the University to consider adopting it as an official replacement to CDCS.

Given the excellence of the University's inspiring faculty and academic programs, I know that I am not alone in my disappointment with what I consider a low regard for usability in many student tools, as well as the lack of communication channels with students to improve them. Throughout the course of this paper, I have shown that the space of course scheduling holds vast potential for innovation, and that CDCS barely scratches that surface. An officially adopted Skedge---or an otherwise substantial overhaul of CDCS---would demonstrate that the University pays attention to its students and to how they use the tools it provides them.

### 2016-04-12 design/search.tex
Small fixes
Analytics

Of course, the most important usability concern for a course explorer/scheduler is being able to effectively \emph{find courses}.

In this section, I will present the \emph{Skedge DSQL}, a domain-specific query language that is based on natural language. Next, I will demonstrate how Skedge leverages the DSQL to handle the three search criteria students have for finding courses better than CDCS does.

@@

In the spirit of this chapter's theme, Skedge's search method was, again, primarily designed as a reaction to CDCS's. CDCS's search method is a 15-field form (see Figure \ref{fig:cdcs-search}), of which I only found myself regularly using two (one of them being the \emph{required} ``Year/Term'' field). This prompted me to closely examine the fields to a) determine redundancies between them and b) find how to make some of the valuable filter fields more usable. From this came Skedge's unified, natural language based search method, which I call the \emph{Skedge Domain-Specific Query Language (Skedge DSQL)}. Figure \ref{fig:sk-search} is a list of example possible searches shown to users as they type.

@@

\begin{enumerate}
  \item \emph{Subject} (department).
  \item \emph{Course} (department code and/or course number, e.g. ``csc 171'').
  \item \emph{Title} (course title).
\end{enumerate}

@@

    In addition, once learned and remembered, using a natural language based query language can be faster and more intuitive than clicking on form fields. And more importantly, the Skedge DSQL is more easily extendable as new search features are invented. For CDCS, the more form fields that are added to the sidebar, the less usable its user interface becomes. For Skedge, while it may take longer for users to learn a bigger DSQL, there is no issue with crowding user interface real estate.

>>>>

The most important usability concern of all for a course explorer/scheduler is being able to effectively \emph{find courses}. In this section, I will present \emph{SkedgeQL}, a domain-specific query language that is free-form and based on natural language. Next, I will demonstrate how Skedge leverages the DSQL to handle the three search criteria students have for finding courses better than CDCS does.

@@

In the spirit of this chapter's theme, Skedge's search method was, again, primarily designed as a reaction to CDCS's. CDCS's search method is a 15-field form (see Figure \ref{fig:cdcs-search}), of which I only found myself regularly using two (one of them being the \emph{required} ``Year/Term'' field). This prompted me to closely examine the fields to a) determine redundancies between them and b) find how to make some of the valuable filter fields more usable. From this came Skedge's unified, natural language based search method, which I call the Skedge Query Language, or \emph{SkedgeQL}. Figure \ref{fig:sk-search} is a list of example possible searches shown to users as they type.

@@

\begin{enumerate}
  \item \emph{Subject} (department)
  \item \emph{Course} (department code and/or course number, e.g. ``csc 171'')
  \item \emph{Title} (course title)
\end{enumerate}

@@

    It has been shown that once learned, natural language based query languages can be faster, more intuitive, and more usable than traditional form-based methods \cite{dsl}. WolframAlpha's hugely successful online free-form search is a notable pioneer in this field \cite{wolfram}.

    Lastly, the Skedge DSQL is more easily extendable as new search features are invented. For CDCS, the more form fields that are added to the sidebar, the less usable its user interface becomes. For Skedge, while it may take longer for users to learn a bigger DSQL, there is no issue with crowding user interface real estate.
